Abstraction and Invariance for Algebraically Indexed Types

### 2012-07-10 paper/section-instantiations.tex

\subsection{Indefinability}
\label{sec:types-indexed-abelian-groups-indef}
\newcommand{\Grp}{\mathit{Grp}}
For proving non-definability results, we
consider the general case of a sort $\mathsf{G}$ with the equational theory of abelian groups.
We assume a group-indexed primitive type $\tyPrimNm{G}$ and
set of primitive operations typed by $\Gamma_\Grp$ that reflect the group structure at the value level,
with identity $1:\tyPrim{G}{1}$, operation
$(\cdot): \forall a,b\mathord:\mathsf{G}.\ \tyPrim{G}{a} \to \tyPrim{G}{b} \to \tyPrim{G}{a\cdot b}$
and inverse $\ ^{-1}: \forall a\mathord:\mathsf{G}.\ \tyPrim{G}{a} \to \tyPrim{G}{a^{-1}}$.
One instance is the sort~$\SynTransl{2}$ with $0$, $(+)$ and $\mathrm{negate}$ operations.

For index-erasure interpretation, we assume a (not necessarily abelian) group $(G, 1, \cdot,
\ ^{-1})$. Let $Z(G)$ be the centre of the $G$: i.e.,~the set of
elements that commute with every other element in $G$. We set
$\tyPrimSem{G} = G$. The primitive operations in $\Gamma_\Grp$ are
interpreted just as the unit, multiplication and inverse operations
of $G$. For each index context $\Delta$, the set
$\relEnv{E}_\Grp(\Delta)$ of relational environments is defined to be
$\{ \rho_{(H,h)} \sepbar H\textrm{ is a subgroup of }(\Delta
\Rightarrow \mathsf{G})/\equiv, h\textrm{ is a group homomorphism }H
\to Z(G) \}$, where
\begin{displaymath}
  \rho_{(H,h)}\ \tyPrimNm{G}\ (e) = \left\{
    \begin{array}{ll}
      \{ \} & \textrm{if}\ e\not\in H \\
      \{ (x, h(e)\oplus x) \sepbar x \in G \} & \textrm{if}\ e\in H
    \end{array}
  \right.
\end{displaymath}

>>>>

\subsection{Indefinability}
\label{sec:types-indexed-abelian-groups-indef}

\newcommand{\Grp}{\mathit{Grp}}
For proving non-definability results, we
consider the general case of a sort $\mathsf{G}$ with the equational theory of abelian groups.
We assume a group-indexed primitive type $\tyPrimNm{G}$ and
set of primitive operations typed by $\Gamma_\Grp$ that reflect the group structure at the value level,
with identity $1:\tyPrim{G}{1}$, operation
$(\cdot): \forall a,b\mathord:\mathsf{G}.\ \tyPrim{G}{a} \to \tyPrim{G}{b} \to \tyPrim{G}{a\cdot b}$
and inverse $\ ^{-1}: \forall a\mathord:\mathsf{G}.\ \tyPrim{G}{a} \to \tyPrim{G}{a^{-1}}$.
One instance is the sort~$\SynTransl{2}$ with $0$, $(+)$ and $\mathrm{negate}$ operations.

For index-erasure interpretation, we assume a (not necessarily
abelian) group $(G, 1, \cdot, \ ^{-1})$. Let $Z(G)$ be the centre of
the $G$ %: i.e.,~the set of elements that commute with every other
%element in $G$. We set 
and $\tyPrimSem{G} = G$. The primitive operations
in $\Gamma_\Grp$ are interpreted just as the unit, multiplication and
inverse operations of $G$. For each index context $\Delta$, the set
$\relEnv{E}_\Grp(\Delta)$ of relational environments is defined to be
$\{ \rho_{(H,h)} \sepbar H\textrm{ is a subgroup of }(\Delta
\Rightarrow \mathsf{G})/\equiv, h\textrm{ is a group homomorphism }H
\to Z(G) \}$, where
\begin{displaymath}
  \rho_{(H,h)}\ \tyPrimNm{G}\ (e) = \left\{
    \begin{array}{ll}
      \{ \} & \textrm{if}\ e\not\in H \\
      \{ (x, h(e)\oplus x) \sepbar x \in G \} & \textrm{if}\ e\in H
    \end{array}
  \right.
\end{displaymath}
